ForestClaw: Hybrid forest-of-octrees AMR for hyperbolic conservation laws

### 2013-02-26 docs/parco13/abstract.tex
Collect some key points

%%%%%%%%%%% End of definitions
\begin{document}
\begin{frontmatter}          % The preamble begins here.
%
%\pretitle{}
\title{Title}
\runningtitle{Running title}
%\subtitle{}

% For one author:
\author[A]{\fnms{Carsten} \snm{Burstedde}%
\thanks{Corresponding author.  E-mail: \texttt{burstedde@ins.uni-bonn.de}}},
\author[B]{\fnms{Donna} \snm{Calhoun}},
\author[C]{\fnms{Kyle} \snm{Mandli}} and
\author[C]{\fnms{Andy R.} \snm{Terrel}}
\runningauthor{C.\ Burstedde et.al.}
\address[A]{Institut f\"ur Numerische Simulation, Universit\"at Bonn, Germany}
\address[B]{Boise State University, Idaho, USA}
\address[C]{Institute for Computational Engineering and Sciences,\\
The University of Texas at Austin, USA}
%
% Two or more authors:
%\author[A]{\fnms{} \snm{}},
%\author[B]{\fnms{} \snm{}}
%\runningauthor{}
%\address[A]{}
%\address[B]{}
%
%%\begin{abstract}

%%\end{abstract}

@@

\cite{BursteddeWilcoxGhattas11}

@@

%%%%%%%%%%% The bibliography starts:
\bibliographystyle{siam}
\bibliography{ccgo}
\end{document}

>>>>

\usepackage{amsmath,amssymb}
\usepackage{cite}

\newcommand{\sR}{\mathbb{R}}

%%%%%%%%%%% End of definitions
\begin{document}
\begin{frontmatter}          % The preamble begins here.
%
%\pretitle{}
\title{ForestClaw:
        Hybrid forest-of-octrees AMR for hyperbolic conservation laws}
\runningtitle{ForestClaw}
%\subtitle{}

% Two or more authors:
%\author[A]{\fnms{} \snm{}},
%\author[B]{\fnms{} \snm{}}
%\runningauthor{}
%\address[A]{}
%\address[B]{}
%
\author[A]{\fnms{Carsten} \snm{Burstedde}%
\thanks{Corresponding author.  E-mail: \texttt{burstedde@ins.uni-bonn.de}}},
\author[B]{\fnms{Donna} \snm{Calhoun}},
\author[C]{\fnms{Kyle} \snm{Mandli}} and
\author[C]{\fnms{Andy R.} \snm{Terrel}}
\runningauthor{C.\ Burstedde et.al.}
\address[A]{Institut f\"ur Numerische Simulation, Universit\"at Bonn, Germany}
\address[B]{Boise State University, Idaho, USA}
\address[C]{Institute for Computational Engineering and Sciences,\\
The University of Texas at Austin, USA}

\begin{abstract}
%
We present a new hybrid paradigm for parallel adaptive mesh refinement (AMR)
that combines the scalability and lightweight architecture of tree-based AMR
with the computational efficiency of patch-based solvers for hyperbolic
conservation laws.  The key idea is to interpret each leaf of the AMR hierarchy
as one uniform compute patch in $\sR^d$ of dimensions $m^d$, where $m$ is
customarily between 8 and 32.  Thus, computation on each patch can be optimized
for speed, while we inherit the flexibility of adaptive meshes.  In our work we
choose the p4est AMR library as mesh backend since it allows to compose the
mesh from multiple mapped octrees, thus enabling us to work with the cubed
sphere and other nontrivial multiblock geometries.
%
\end{abstract}

@@

@@

Experience from integration with large-scale adaptive-mesh PDE solvers.

Design goals: Lightweight, modular, reuse.

Separation of mesh on the one hand from discretization and solvers on the other.

Mesh information is discrete (tree nodes have integer coordinates in
$(0, 2^L($ where $L$ is the maximum allowed refinement level of the tree.

sorted ordering of tree nodes, lookup tables, .

p4est \cite{BursteddeWilcoxGhattas11}

rank as is common with parallelization using the MPI framework
\cite{Forum94, SnirOttoHuss-LedermanEtAl96}.

Challenge: patch neighborhood information is known to the mesh backend
but needs to be used to handle ghost information.

\section*{Hybrid forest-of-octrees AMR}

Iterators over all leafs, optionally restricted to a given level.

same block, same rank: local copy.

neighbor block: permutation of patch points due to non-aligned
coordinate systems

neighbor processor: data needs to be fetched over the network first.

Trees have different coordinate systems.

$L$ is 30 for 2D and 19 for 3D, so it allows for deep hierarchies.

\section*{Patch-based numerics at the leaf level}

\section*{Numerical results}

%%%%%%%%%%% The bibliography starts:
\bibliographystyle{siam}
\bibliography{ccgo}

\end{document}
